\modLP{Identification of} Biological Regulatory Networks from Process Hitting models

### 2014-09-17 parts-tr2global.tex
minor

From \pref{def:focals}, we call a \emph{deterministic sort} \pref{pro:deterministic-sort} a sort $a$
that has a single focal process for any possible configuration of its predecessors in the scope of
$L_a$.

>>>>

We call a \emph{deterministic sort} \pref{pro:deterministic-sort} a sort $a$
that has a single focal process for each possible configuration of its predecessors in the scope of
$L_a$.
